Reparametrization of COM-Poisson Regression Models with Applications in the Analysis of Experimental Data

### 2017-11-14 article.Rnw
Improve conclusion section

In this paper, we argued the parametrization of COM-Poisson distribution
to analyse dispersed count data. We proposed a novel reparametrization
based only mean approximation indicated by \cite{Shmueli2005}. The
likelihood-based method to estimation and inference is presented. We
assess the properties of these estimators by a simulation
study. Applications of the proposed model are showed by three case
studies with over, under and equidispersed counts. In the data analysis
we compared standard Poisson, original COM-Poisson, reparametrized
COM-Poisson and quasi-Poisson models.

We computed the quadratic errors for the mean approximation. The results
showed that it is well accurate supports our proposed
reparametrization. The results of a simulation study showed that the
estimators of the regression and precision parameters are consistent and
unbiased and asymptotically unbiased respectively. The empirical
coverage rates of the confidence intervals for the parameters, compute
by the asymptotic distribution of the estimators, are close to the
nominal level for sizes greater than 100. The worst scenario is when we
have small sample size and strong overdispersed counts. In general, we
recommend the use of Wald intervals for computational simplicity and
good results.

The data analysis in the case studies has shown that COM-Poisson is a
suitable distribution for over, under and equidispersion situations. The
observed empirical correlation between regression and precision
parameters suggest the orthogonality between $\mu$ and $\phi$ in
COM-Poisson$_\mu$ distribution against the original parametrization. Due
to this feature the computational procedure is faster under the
reparametrized model. Another advantage, perhaps the main, of the
reparametrization is that the estimated regression parameters have
interpretation of rate ratios, same of the Poisson model. In comparison
of the quasi-Poisson approach the results was similar in both
simulations, nevertheless the COM-Poisson is a full parametric model,
allowing the calculation of probabilities for example.

In general, the results presented by the reparametrized COM-Poisson
models were satisfactory and superior to the conventional
approaches. Therefore, its use in the analysis of count data is
encouraged. The computational routines for fitting of original and
reparametrized COM-Poisson models are available in the supplementary
material\textsuperscript{\ref{papercompanion}}.

There are many possible extensions and possible topics for further
investigation to model discussed in the present paper, including
simulation study to assess model robustness against distribution
miss-specification, asses theoretical approximations for
$Z(\lambda, \nu)$ (or $Z(\mu,\phi))$, in order to avoid the selection of
sum's upper bound, propose a double GLM based on the reparametrized
COM-Poisson model and a accommodate random effects since we have a model
parametrized on mean.

>>>>

In this paper, we presented a novel parametrization of the COM-Poisson
distribution and the associated regression model. The novel
parametrization was based on a simple asymptotic approximation for the
expectation and variance of the COM-Poisson distribution. The main
advantage of the proposed reparametrization is the simple interpretation
of the regression coefficients in terms of the expectation of the
response variable as usual in the generalize linear models
context. Thus, it is possible to compare the results of the COM-Poisson
model with the ones from standard approaches as the Poisson and
quasi-Poisson regression models. Furthermore, in the novel
parametrization the COM-Poisson distribution is indexed by the
expectation $\mu$ and an extra dispersion parameter $\phi$ whose our
data analysis suggest to be orthogonal.

We evaluated the accuracy of the asymptotic approximations for the
expectation and variance of the COM-Poisson distribution by considering
quadratic approximation errors.  The results showed that the
approximations are accurate for a large part of the parameter space of
the parameters $\mu$ and $\phi$, which in turn support our
reparametrization.  We carried out a simulation study to assess the
properties of the reparametrized COM-Poisson model to deal with
different levels of dispersion as well as the properties of the maximum
likelihood estimators. The results of our simulation study suggested
that the maximum likelihood estimators of the regression and dispersion
parameters are unbiased and consistent.  The empirical coverage rates of
the confidence intervals computed based on the asymptotic distribution
of the maximum likelihood estimators are close to the nominal level for
sample size greater than $100$.  The worst scenario is when we have
small sample sizes and strong overdispersed counts.  In general, we
recommend the use of the asymptotic confidence intervals for
computational simplicity.

The data analyses have shown that the COM-Poisson regression model is a
suitable choice to deal with non equidispersed count data.  The observed
empirical correlation between the regression and dispersion parameter
estimators suggest orthogonality between $\mu$ and $\phi$ in
COM-Poisson$_\mu$ distribution. Thus, the computational procedure based
on the proposed reparametrization is faster than in the original
parametrization.

In general, the results presented by the reparametrized COM-Poisson
models were satisfactory and comparable to the convential approaches.
Therefore, its use in the analysis of count data is encouraged. The
computational routines for fitting the original and reparametrized
COM-Poisson regression models are available in the supplementary
material\textsuperscript{\ref{papercompanion}}.

There are many possible extensions to the model discussed in this paper,
including simulation studies to assess the model robustness against
model misspecification and to asses the theoretical approximations for
$Z(\lambda, \nu)$ (or $Z(\mu,\phi))$. Another simple extension of the
proposed model is to model both $\mu$ and $\phi$ parameters as functions
of covariate in a double generalized linear models framework.  Finally,
the reparametrized version of the COM-Poisson model also encourages the
specification of generalized linear mixed models using this
distribution.
